---
title: "Recommendations for your mediation analysis"
output: html_document
params:
   Objective : NA
   VarType : NA
   ConstraintVar : NA
   ConstraintConf : NA
   ConstraintPos : NA
   Interaction : NA
   Estimands: NA
   Decomposition : NA
   Methodes : NA
   Assumptions : NA
   Packages : NA

---

# Résumé de vos réponses

<b> Objectives </b>
`r params$Objective`
<br>

<b> Variable types </b>
```{r, echo=F}
kableExtra::kable_styling(knitr::kable(params$VarType), full_width = F, position = "left")
```

<b> Constraints on variables of interest </b>
```{r, echo=F}
kableExtra::kable_styling(knitr::kable(params$ConstraintVar), full_width = F, position = "left")
```

<b> Constraints on confounders </b>
```{r, echo=F}
kableExtra::kable_styling(knitr::kable(params$ConstraintConf), full_width = F, position = "left")
```

<b> Positivity </b>
```{r, echo=F}
kableExtra::kable_styling(knitr::kable(params$ConstraintPos), full_width = F, position = "left")
```

<b> Interaction entre l'exposition et le médiateur </b>
```{r, echo=F}
kableExtra::kable_styling(knitr::kable(params$Interaction), full_width = F, position = "left")
```

# Recommendations

## Estimands

`r params$Estimands`

## Decomposition
`r params$Decomposition`

## Methods
`r params$Methodes`

## Assumptions
`r params$Assumptions`

## R packages 
`r params$Packages`
